\section<presentation>*{参考文献}

\frame{
  \transdissolve
  \frametitle<presentation>{参考文献}

  \beamertemplatebookbibitems

  \begin{thebibliography}{10}

  \bibitem{TeX}
    Douglas C. Giancoli
    \newblock {Physics for scientists and Engineers with Modern Physics}.
    \newblock {Higher Education Press}
    \pause

   \beamertemplatearticlebibitems

  \bibitem{userguide}
    Celia A. de Sousa and Vitor H. Rodrigues
    \newblock {Mass redistribution in variable mass systems}
    \newblock {Eur.J.Phys. 25(2004) 41-49}
    \pause

  \beamertemplatearticlebibitems

  \bibitem{userguide}
    Mario J. Pinheiro.
    \newblock {Some Remarks about Variable Mass Systems}
    \newblock {Eur.J.Phys. 25(2004) L5-L7}
    %\newblock {\em www.med.harvard.edu/AANLIB/home.html .}, August 28, 2009.
    \pause
  \end{thebibliography}
}


\frame{
  \transdissolve
  \frametitle<presentation>{参考文献}

  \beamertemplatebookbibitems

  \begin{thebibliography}{10}

  \beamertemplatearticlebibitems
\bibitem{userguide}
   Livija J. Cveticanin.
    \newblock {DYNAMICS OF THE SYSTEM WITH DISCONTINUAL MASS VARIATION.}
    \newblock {Theoretical and Applied Mechanics Kopaonik, Serbia, April 10-13, 2007}
    \pause

\bibitem{userguide}
   F. O. EKE and T. C. MAO.
    \newblock {On the dynamics of variable mass systems.}
    \newblock {International Journal of Mechanical Engineering Education Vol 30 No 2}
    \pause

  \beamertemplatearticlebibitems
\bibitem{userguide}
   Jose Flores, Guillermo Solovey, Salvador Gil.
    \newblock {Variable mass oscillator.}
    \newblock {Am. J. Phys. 71(7), July 2003}
    \pause
  \end{thebibliography}
}

\frame{
  \transdissolve
  \frametitle<presentation>{参考文献}

  \beamertemplatebookbibitems

  \begin{thebibliography}{10}

  \beamertemplatearticlebibitems
  \bibitem{userguide}
     University of California at Berkeley, Physics Department.
    \newblock {Physics Lecture Demonstrations.}
    \newblock {\em http://www.mip.berkeley.edu/physics/physics.html}
    \pause

  \beamertemplatearticlebibitems
  \bibitem{userguide}
     袁建飞
    \newblock {变质量系统动量变化率解析方程的研究验证分析}
    \newblock {毕业论文}
    \pause
  \end{thebibliography}
}